Computing volume via non-linear rectangular prisms

### 2019-08-01 Cav2D/article-template.tex
new notation for cavalieri --- semi nice

@@

\noindent
Intersestingly, the definition in Eq.~\eqref{??} can also be formulated via vector calculus notation. As will become apparent later on in the article extending the definition of the Cavalieri integral as it appears in ?? into $\mathbb{R}^3$ is problematic. However,
if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.

\noindent
Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
\begin{equation}
\label{eq:pat_rel}
\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
\end{equation}
We can rewrite Equation~\eqref{eq:pat_rel} as
\begin{equation}
\label{eq:t_func}
c_y(t) = f(x_i^1 + c_x(t)),
\end{equation}
which highlights the fact that $t$ is a function of $x_i^1$. If we substitute $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain
\begin{equation}
\label{eq:h_func}
x_i^2 = x_i^1 + c_x\circ t(x_i^1).
\end{equation}
Note that Equation~\eqref{eq:h_func} is nothing more than the function $h$ expressed in terms of $t$, i.e. $x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1)$.
Equation~\eqref{eq:h_func} implies

>>>>

Let $\mathbf{c}(t) = \left <c_x(t),c_y(t) \right>$ be the vector equation of $a(y)-a$. The notation which we have been using to denote a Cavalieri integral up until now 
in the paper was first proposed by Ackermann. Going forward in this paper, however, we propose making use of the following alternative notation:
\begin{equation}
\label{eq:new_def_cavalieri}
\int \limits_{\mathcal{C}} f(x)~dx := \int_{a(y)}^{b(y)}f(x)~dx,
\end{equation}
with $\mathcal{C} = \{\mathbf{c}(t),[a,b]\}$. Note that $\left<a,0\right> + \mathbf{c}(t)$ and $\left<b,0\right> + \mathbf{c}(t)$ are the vector equations of $a(y)$ and 
$b(y)$. The reason for this change in notation will become clear to the reader at a later stage. In turns out, that we can use $\mathbf{c}(t)$ to construct $h(x)$ via:
\begin{equation}
\label{eq:h_func}
x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1).
\end{equation}

\noindent
We will now show that this is indeed the case. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
\begin{equation}
\label{eq:pat_rel}
\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
\end{equation}
We can rewrite Equation~\eqref{eq:pat_rel} as
\begin{equation}
\label{eq:t_func}
c_y(t) = f(x_i^1 + c_x(t)).
\end{equation}
We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain Equation~\ref{eq:h_func}.

In turns out that $h$ can be constructed

as the reader progresses through the paper. As will become apparent later on in this paper defining your Cavalieri integral in terms of $\mathbf{c}(t)$ instead of 
$a(y)$ makes it trivial to extend its defintion into $\mathbb{R}^3$.

In Equation~\eqref{eq:new_def_cavalieri}, we denote the $\{\mathbf{c}(t),[a,b]\}$ via $\mathcal{C}$. Furthermore, $\mathbf{c}(t)$ denotes the vector equation of 
$a(y)-a$.

an alternative notation

@@

\noindent
Intersestingly, the definition in Eq.~\eqref{??} can also be formulated via vector calculus notation. As will become apparent later on in the article extending the definition of the Cavalieri integral as it appears in ?? into $\mathbb{R}^3$ is problematic. However,
if the definition in ?? is first re-expressed in vector calculus notation then it becomes trivial to extend it into $\mathbb{R}^3$.\\

\noindent
We will now show that this is indeed the case. Note that, for every coordinate $(x_i^1,x_i^2) \in [a,b] \times [a',b']$ there exists a unique $t\in\mathbb{R}$ such that
\begin{equation}
\label{eq:pat_rel}
\left <x_i^2,f(x_i^2) \right > = \left <x_i^1,0 \right> + \left<c_x(t),c_y(t) \right >.
\end{equation}
We can rewrite Equation~\eqref{eq:pat_rel} as
\begin{equation}
\label{eq:t_func}
c_y(t) = f(x_i^1 + c_x(t)).
\end{equation}
We can now solve for $t$ in Equation~\eqref{eq:t_func} in terms of $x_i^1$. If we substitute the solution $t(x_i)$ into Equation~\ref{eq:pat_rel} we obtain
\begin{equation}
\label{eq:h_func}
x_i^2 = x_i^1 + c_x\circ t(x_i^1).
\end{equation}
Note that Equation~\eqref{eq:h_func} is nothing more than the function $h$ expressed in terms of $t$, i.e. $x_i^2 = h(x_i^1) = x_i^1 + c_x\circ t(x_i^1)$.
We can, therefore compute $h(x)$ from $\mathbf{c}(t)$ and as such we can can define the Cavalieri integral in terms of $\mathbf{c}(t)$ instead of $a(y)$. In light 
of this observation we propose the following alternative notation to denote a Cavalieri integral 
\begin{equation}
\int  
\end{equation}

Equation~\eqref{eq:h_func} implies
